ud\hat& {d   &on t}op of charbs & i &n

Consubsein Q


pdflatex -output-directory=$(BUILD_DIR) $(DOCUMENT).tex 2>&1 | tee $(LOG)

$$ \ubsein Q
Refeubsein Q
8darubsei_{q\in []QQ

\sum{}
\sum{}

R111ubsein Q + \sum_{p \in Q} P(q|p, k) \hat{\lambda_}_{k}(p)
h \amsmathH
A(h,q) \eq 3\begubsein Q
ubsein Q
ubsein Q




ubsein Q

ubsein Q
ubsein Qlanguages such as TOSCA and HOT can be evaamou (or called traffic in this draft)nt of requests of luated for possible adoption or ne:

\begin{itemize}
    \item Invalid packets So can drops based on its ACL e.g. firewall. This is not the focus of our valid packets.


    \item Some functions can add redundant packets. For example, the network recoder.

    \item Some functions can \textbf{reduce} the number of output packets \textbf{without} significantly impact the
        end-to-end service. Reduant packets can be used to fix channel losses with FEC code. However, we focus on the
        wired domain of the latency budget illustrated in the CALVIN paper. Here the physical1 hosts are normally
        connected with reliable wired connections, the channel losses are

\end{itemize}
ubsein Q
input.
However, there are scenarios where the ooutput of the queue p is not equal the ineligible

can be ignored.

ubsein Qtical for telecommunication network operators who typically reqPossibility 77a
ubsein Q{2}$ the cloud service provide kss vs Stateful Mic\\ r rvice design

ubsein Q







ubsein Q
ubsein Q
ubsein Q
ubsein  =sein Q
ubsein Q
ubsein Q

ubsein Q
ubsein Q
from outside the system or from other queues. And the processing \tex{of each }queue does not change  amount of the
required to the next queue\textbf{, therefore, stor}e and forward is usedanalytics  \cite{an}.

is
    \end{equation}

    ubse(q)Q
    ubsein Q
    ubsein Q


    ubsein sQ
    forsein Q
    ubsein Q
    ubsein Q
    ubsein Q
    ubsein Q
    ubsein Q
    ubsein Qwxfxz20180315lovewxfxz20180315lovewxfxz20180315lovewxfxz20180315lovecui

    ubsein Q

    ubsein Qe necessary to run each service, the NFV orchestrator has to make three main
    ubsein Q

    ubsein Q Dear Patrick,

    ubsein Qical hosts have to run the required VNFs.
    ubsein Q
    ubsein Qomputational capabilities of each host have to be shared between VNFs
    ubsein Qred between VNFs (Service function chaining)
    ubsein Q

    ubsein Qg urgentlydx
    ubsein Q

    ubsein Q
    ubsein Qate e77Arrival rates at q of service kseparate logic for handling it.lsls
    ubsein Q
    ubsein Q

    ubsein Qents to this model}% \setlength\itemseq{1em
    ubsein Qents_to_this_model}

    ubsein Qjjjjjjjjjjjjjjjjjjjjjjjjjjjjjjjjjjjjjjjj $k2/belong
    ubsein Qtween itemize

    ubsein Q
    ubsein Q
    ubsein QDear Giang, he is currently working as SHK of Robert. Therefore, I am not the supervisor
    ubsein Q

    ubsein Qobert and let him talk to Andera about the transponder ?
    ubsein Q
    ubsein Q
    ubsein Q
    ubsein Qso ask him to update the STOA. :smil5

    ubsein Q
    ubsein Q
    ubsein Qded service classes. For example. $K$ =\{ video streaming, gaming \}
    ubsein Qtionolor

    ubsein Qd Complexity
    ubsein Q


    ubsein Q
    ubsein QPareto improvements can be made, in which case we are assumeed to have reached Pareto
    ubsein Q
    ubsein Q The key problem here is the \textbf{congestion}
    ubsein Qquations}%
    ubsein Qquations}

    ubsein Qment of impossibility of improving one variable without harming other variables in the subject of
    ve.
    2
    fee


    ubsein Qoptimizationsp
    openst

    .ubsein Qon of Pareto efficency has been applied to the selection of alternatives in engineering and
    ubsein Q

    ukarino zhihuchinese2212Akraino Ic
    angxiangmu
    Iukarino zhihuchinese2212Akraino Ic
    .bsein Qally defined concept used to determine when an allocation is### Use in Engineering

    ubsein Q






    ubsein  Qservice graphs and six
    Q


    NAP Icangxiangmu
    Iukarino zhihu
    chinese2212Akraino Ic
    typical33_topo.pdfject detection service.Tung, thanks so much for your explaination of your ideas and sorry for the
    botherDue to Giang's idea of cooperation, I want to understand more about your work. Unfortunately, just from my point
    of view, you are solving problems  onlReview


    s

    2&7OPNAP
    ONAPein Qn perceived arrival rate in response to the other player'squeue_model_ alloca_333tions.2p1]siexample
    ubsein Q
    ubsei<F2>
    jjjjjjjjjjjjjjjjjjjjjjjjjjjjjjjjjjjjjjjjjjjONAP vs OPNFV
    Ic<F2
    jjjjjjjjjjjjjjjjjjjjjjjjjjjjjjjjjjjjjjjjjjjONAP vs OPNFV
    NAP is addressing these challenges by developing global and massive scale
    (multl
    ls
    26ls
    22VIM clearwater
    44s<F5>1i-site and multi-VIM22 automation capabilities for both physical and
    virtual network elements. It facilitates service agility by supporting
    data models for rapid service and resource deployment, and providing a
    common set of Northbound REST APIs that are open and interoperable, and by
    supporting model driven interfaces to the networks. ONAP's modular and
    layered nature improves the interperability and simplifies integration,
    allowing it to support multiple VNF environments by integrating with
    multiple VIMs, VNFMs, SDN Controllers and even legacy equipment. ONAP's
    consolidated VNF requirements publication will enable commercial
    development of ONAP-compliant VNFs. ONAP's use of standard models reduce
    integration and deployment costs of heterogenous eqqquipment, while
    minimizing management fragmentation.















    The ONAP platform allows end-user organization and their network/cloud
    providers to collaboratively instantiate network elements and services in
    a dynamic, closed control loop processes, with real-time, response to
    actionable events.

    * A robust design framework that allows specification of the service in
    all aspects --- modeling the resources and relationships that make up the
    service, specifying the policy rules guide the service behavior.
    An orchestration and control framework, policy driven to provide automated
    instantiation of the service when needed and managing service demands in
    an elastic manner.
    An analytic framework that closely monitors the service behavior during
    the service lifecycle based on the specified design, analytics and
    policies to enable response as required from the control framework, to
    deal with situations ranging from those that require healing to those that
    require scaling of the resources to elasitically adjust to demand
    variations.


    To achieve this, ONAP decouples the details of specific services and
    cui
    2
           /tilix
    7
    technologies from the common information models.w@898pacui
    3
    st








    )
    Ic<Fnd OPNFV
    3784and virtual netwo 1rk functions nux terminal emulator that will enable software, network, IT and cloud developers to rapidly automate new
    services and support complete lifecycle management. By unifying member resources, ONAP is acclerating the development of
    a vibrant ecosystem around a globally shared architecture and implementation for network automation -- with an open
    standards focus -- faster than any one product cloud on its own.

    ## White Paper2>
    ubsein Q \\

    ubsein Q
    ubsein Q
    ubsein Q defined and imagined by yourself. They are somehow not that high level in theor(neither) and formulation)
    My major was Information theory during the BathlerBachelor, so I understand theory nor thatdeploI can not get the key
    point from you currendifficult to have any cooperation. I cooperate with Justus now for reinforcement
    learning based routing and serverless NFV. I know you just wantte
    terminal
    9dtillixxIujjjjjjjjjjjjjjjjjjjjjjjjjjkkkkkkkktunHi IujjjjjjjjjjjjjjjjjjjjjjjjjjkkkkkkkktunHi
    IujjjjjjjjjjjjjjjjjjjjjjjjjjkkkkkkkktunHi IujjjjjjjjjjjjjjjjjjjjjjjjjjkkkkkkkktunHi
    IujjjjjjjjjjjjjjjjjjjjjjjjjjkkkkkkkktunHi IujjjjjjjjjjjjjjjjjjjjjjjjjjkkkkkkkktunHi
    IujjjjjjjjjjjjjjjjjjjjjjjjjjkkkkkkkktunHi IujjjjjjjjjjjjjjjjjjjjjjjjjjkkkkkkkktunHi cui
    3
    tilixmto get your PhD. So do I :pou
    But my targets are A level conferences and top journals :wink
    Thanks
    wxfxz20180315love.
    y

    six
    ls
    ls -al
    hackQls
    ls
    ls -al
    ls
    ls
    htop
    <F3>tilix
    <F3>tilix
    qls
    kk
    ls
    ls
    ls -al
    lsQls
    tree tm
    ls
    pacui
    4
    terminator
    wxfxz20180315love.
    y

    n for your explaination on Friday.
    jjjjjjjjj22Qdrawio
    absein Q
    \ubsein Q
    begin{aligned}
    ubsein Q
\end{aligned}
ubsein Q
ubsein Q

ubsein Q
ubsein Q
ubsein Q
ubsein Q
ubsein Q

ubsein Q
ubsein Q
ubsein Q
ubsein Q
ubsein Q
ubsein Q
ubsein Q

ubsein Q

ubsein Q
ubsein Qches
ubsein Q
ubsein Q
ubsein Q approach firstly. My idea is also pla "beat the MILP STOA approaches with more adaptive
ubsein Qlso iapproaches that use evolutionary algorithms instead of greedy algorithms to develop
ubsein Qns. We can exchange ideas and discuss about the algorithms next Monday. Anoant and
ubsein Q is for the state synchronization. If y              The trend is to decouple the stThe
ubsein Qnistic or probabilistic, depending on the use-cases.
ubsein Qnce model
ubsein Q
ubsein Q from Intel, it is somehow bette, documented and updated than heterogenous  academic
ubsein Qer, no updates any more...
ubsein Qn the example directory to play with. e.g. NATls
ubsein Q
ubsein Q
ubsein Q
ubsein Q
ubsein Qop and move to fast path on real t the same code.mature tools like Snort. Maybe it is


ubsein Qcan also use this as one example for you golang learning, so do I ^_^game theasier to customize later for our own purposes
ubsein Q
ubsein Qaper or reference of the game-theory approach from Nokia? t st
ubsein Q
ubsein QarIntel has pushed a video about the
\21
tex

ubsein Q). (in DPDK conference
